The Processing of American Indian/Alaska Native Children through non-Tribal

### 2019-12-18 ms.rmd
add white data

```{r include=F}
rm(list=ls()); gc()
library(tidyverse)
source("lifetable.r")

pop<-read_csv("./data/pop_aian_nat.csv")
afcars<-read_csv("./data/afcars_subset.csv",
                 col_types = cols(stfcid="c"))

afcars_all<-read_csv("./data/afcars_id_xwalk.csv",
                     col_types = cols(stfcid="c"))

@@

xwalk<-ncands_xwalk %>% 
  left_join(afcars_all) %>% 
  filter(!(is.na(fy))) %>% 
  select(stfcid, rptdt, fy) %>% 
  rename(fc_year = fy)

@@

```{r ncandstables.pop}
ncands_first<-ncands %>% 
  select(.imp, chid, chage, rptdt) %>% 
  group_by(chid) %>% 
  filter(rptdt==min(rptdt)) %>% 
  distinct() %>% 
  ungroup() %>% 
  mutate(year = year(rptdt))

ncands_first_nat<-ncands_first %>% 
  group_by(chage, year) %>% 
  summarise(var = n()) %>% 
  rename(age = chage) %>% 
  left_join(pop) %>% 
  ungroup()

@@

investigation_tables %>% 
  filter(age==17) %>% 
  ggplot(aes(x=year, y = c)) +
  geom_line()

>>>>

```{r include=F}
rm(list=ls()); gc()
library(tidyverse)
library(lubridate)
source("lifetable.r")

pop<-read_csv("./data/pop_nat.csv")
afcars<-read_csv("./data/afcars_subset.csv",
                 col_types = cols(stfcid="c"))

@@

xwalk<-read_csv("./data/xwalk_merged.csv")

@@

```{r ncandstables.pop}
### identify first report
ncands_first<-ncands %>% 
  select(.imp, race_ethn, stfcid, chage, rptdt) %>% 
  group_by(stfcid) %>% 
  filter(rptdt==min(rptdt)) %>% 
  ungroup() %>% 
  distinct() %>% 
  mutate(year = year(rptdt))

ncands_first_nat<-ncands_first %>% 
  group_by(.imp, race_ethn, chage, year) %>% 
  summarise(var = n()) %>% 
  ungroup() %>% 
  rename(age = chage) %>% 
  left_join(pop) %>% 
  filter(age < 18)

@@

investigation_tables %>% 
  filter(age==17) %>% 
  ggplot(aes(x=year, y = c, color = race_ethn)) +
  geom_line()
